Constructing the transition graphs of interacting hysterons

### 2022-06-09 Paper_draft.tex

We here show how the possible avalanches are evaluated for a given base graph.We first describe how one systematically constructs the possible avalanches of length $l=2$ for a base graph. We then generalize our method to avalanches of any length $l$\\

@@

Thus far, we have only considered avalanches of length $l=2$. We now describe how we construct graphs that have avalanches of length $l=3$ based on the graphs that have only $l=2$.\\
Suppose that we have a graph containing only $l=2$ avalanches. Similarly to how we can find $l=2$ avalanches for a base graph by evaluating combinations of incoming and outgoing transitions from the state $S^{(1)}$, we can construct possible $l=3$ avalanches by finding all combinations of $l=2$ avalanches and outgoing $l=1$ transitions for the given graph. From the possible $l=3$ avalanches, we can again construct a list of candidate graphs.\\
We now ask which $l=2$ graphs should be used as our new 'base' for the $l=3$ graphs. It is insufficient to use only the $l=2$ graphs that are themselves realizable, as it is not guaranteed that a derived $l=3$ graph will also be impossible.\\
We observe that, when extending a $l=2$ avalanche to a $l=3$ avalanche, most of the conditions required for the $l=2$ avalanche are still included in the conditions for the $l=3$ avalanche (see SI). The only exception is the final set of relaxation inequalities that describes the stability of the state $S^{(2)}$, which is stable for the $l=2$ transition but unstable for the $l=3$ transition. As a result, we can predict that for a $l=2$ graph of which any of the first $l-1$ relaxation inequalities are incompatible, any derived graphs with longer avalanches must also be impossible.\\

@@

We now generalize our method. To find all graphs with avalanches of length $l$, we construct the graphs for $l-1$, and divide the graphs into the three groups as described. We then construct all possible $l=l$ candidate graphs for each of the $l=l-1$ graphs in the first two groups. We can thus iterate over $l$ to find all possible graphs. Our algorithm terminates when none of the graphs belonging to the first and second groups have any possible avalanches of length $l$.

>>>>

We here show how the possible avalanches are evaluated for a given base graph.We first describe how one systematically constructs the possible avalanches of length $l=2$ for a base graph. We then generalize our method to find graphs containing avalanches of any length $l$.\\
To help our notation, we define $L$ as the length of the longest avalanche in a graph. For example, $L=2$ denotes a graph that contains at least one avalanche of length $l=2$, and no $l=3$ avalanches. In particular, $L=1$ denotes a base graph.\\

@@

Thus far, we have only considered $L=2$ graphs. We now describe how we construct graphs that have avalanches of length $L=3$ based on the $L=2$ graphs.\\
Suppose that we have a $L=2$ graph. Similarly to how we can find $l=2$ avalanches for a base graphs by evaluating combinations of incoming and outgoing transitions, we can construct possible $l=3$ avalanches by finding all combinations of $l=2$ avalanches and outgoing $l=1$ transitions for the given graph. From the possible $l=3$ avalanches, we can again construct a list of candidate graphs.\\
We now ask which $L=2$ graphs should be used as our new 'base' for the $L=3$ graphs. It is insufficient to use only the $L=2$ graphs that are themselves realizable, as it is not guaranteed that a derived $l=3$ graph will also be impossible.\\
We observe that, when extending a $l=2$ avalanche to a $l=3$ avalanche, most of the conditions required for the $l=2$ avalanche are still included in the conditions for the $l=3$ avalanche (see SI). The only exception is the final set of relaxation inequalities that describes the stability of the state $S^{(2)}$, which is stable for the $l=2$ transition but unstable for the $l=3$ transition. As a result, we can predict that for a $L=2$ graph of which the base inequalities and the first set of relaxation inequalities are incompatible, any derived graphs with longer avalanches must also be impossible.\\

@@

We now generalize our method. To find all  $L=l$ graphs, we construct the graphs for $L=l-1$, and divide the graphs into the three groups as described. We then construct all $L=l$ candidate graphs for each of the $l=l-1$ graphs in the first two groups. We can thus iterate over $L$ to find all possible graphs. Our algorithm terminates when none of the graphs belonging to the first and second groups have any possible avalanches of length $l$.
